A state of the art end-to-end speech recognition algorithm with a homogenous structure.

### 2019-05-13 none_feedback_sequence_classifier/doc/main.tex
Updates the paper

In this section, we review well-known {\it sequence-to-sequence} algorithms
used in speech recognition.
\cite{
j_chorowski_nips_2015_00, 
a_graves_corr_2012_00, 
y_he_icassp_2019_00,
r_prabhavalkar_interspeech_2017_00}. 
A sequence-to-sequence
model maps a sequence of input acoustic features into a sequence 
of graphemes or words \cite{r_prabhavalkar_interspeech_2017_00}. 
We denote a sequence of input acoustic feature vectors by 
$\mathcal{X}_{0}^{M-1}$ and a sequence of target labels by 
$\mathcal{Y}_{0}^{L-1}$:
\begin{subequations}
  \begin{align}
    \mathcal{X}_{0}^{}  =  
      \left\{\vec{x}[0], \, \vec{x}[1], 
        \, \cdots, \, \vec{x}[M-1] \right\},  \\
    \mathcal{Y}_{0}^{}  =  
      \left\{y_0, \, y_1, \,  \cdots, \, y_{L-1} \right\},
  \end{align}
\end{subequations}
where $M$ is the number of frames in the input feature sequence and
$L$ is the number of labels in the output target sequence. In Fig. 
\ref{fig:ctc_diagram} $\sim$ \ref{fig:attention_diagram}, we show
block diagrams of CTC \cite{a_graves_icml_2006_00}, 
RNN-T \cite{a_graves_corr_2012_00, a_graves_icassp_2013_00}, and 
the attention-based model 
\cite{
j_chorowski_nips_2015_00,
w_chan_icassp_2016_00} respectively. CTC in Fig. \ref{fig:ctc_diagram} 
and RNN-T in Fig. \ref{fig:rnn_t_diagram} are {\it frame-synchronous}, 
which means that the ASR system generates the output target for each 
input frame.

\subsection{Connectionist Temporal Classification}

@@

@@

\subsection{Neural Network Structure}
Fig. \ref{fig:fsc_diagram} shows the entire structure of the FSC. 
As shown in this figure, LSTM layers and max-pool layers
are interleaved from the bottom layer up to the third max-pool layer.

In Fig. \ref{fig:fsc_diagram}, speech features $\vec{x}[m]$ are sampled 
at every 10 {\it ms}, which is the usual speech feature frame rate  
in speech recognition
\cite{x_huang_prentice_hall_2001_00, c_kim_taslp_2016_00},
Using three two-to-one max-pool layers, $\vec{z}[p]$ has a frame period 
of 80 {\it ms}.  
The relationship between the temporal index $p$ in $\vec{z}[p]$ and 
$m$ in $\vec{x}[m]$ is given by: 
\begin{align}
  p = \lceil m / 8 \rceil \label{eq:def_p}
\end{align}

@@

\subsection{Training of the Feedback Sequence Classifier}
In this section, we describe how to train FSC. The first step is making an
alignment using the N-best alignment. The second step is updating the
neural network parameters using the Cross Entropy (CE) criterion.

@@

The first step is finding the optimal frame-synchronous sequence
$\mathcal{Z}$

@@

>>>>

In this section, we review well-known {\it sequence-to-sequence} algorithms
used in speech recognition.
\cite{
j_chorowski_nips_2015_00, 
a_graves_corr_2012_00, 
y_he_icassp_2019_00,
r_prabhavalkar_interspeech_2017_00}. 
A {\it sequence-to-sequence}
speech recognizers maps a sequence of input acoustic features into a sequence 
of graphemes  \cite{j_chorowski_nips_2015_00, w_chan_icassp_2016_00} or words 
\cite{r_prabhavalkar_interspeech_2017_00}. 
We denote a sequence of input acoustic feature vectors by 
$\mathcal{X}_{0}^{M-1}$ and a sequence of target labels in 
{\it one-hot vector} representation by 
$\mathcal{Y}_{0}^{L-1}$ as shown below:
\begin{subequations}
  \begin{align}
    \mathcal{X}_{0}^{M-1}  =  
      \left\{\vec{x}[m]
          \Big| 0 \le m \le M - 1, \; \vec{x}[m] \in \mathbb{R}^d \right\},  
    \label{eq:input_seq} \\
    \mathcal{Y}_{0}^{L-1}  =  
      \left\{\vec{y}_l  \Big| 0 \le l \le L-1, \; \vec{y}_l \in \mathbb{V} \right\}, 
    \label{eq:target_label}
  \end{align}
\end{subequations}
where $M$ is the number of frames in the input feature sequence,
$d$ in \eqref{eq:input_seq} is the dimension of the input feature.
$L$ is the number of labels in the output target sequence,
 and $\mathbb{V}$ in \eqref{eq:target_label} is the set of output
labels, which may be graphemes 
\cite{j_chorowski_nips_2015_00,
w_chan_icassp_2016_00},
subword units \cite{
a_zeyer_interspeech_2018_00,
c_chiu_icassp_2018_00},
 and words \cite{h_soltau_interspeech_2017_00}.
Note that the sequence index in \eqref{eq:input_seq} is a frame
index, whereas the sequence index in \eqref{eq:target_label} is 
label index. Depending on whether the neural network generates
the inference output for every frame or not, there are following
categories:

\begin{itemize}
  \item {\bf Label-synchronous inference} In this category, the 
neural network generates the inference output $\widehat{\vec{y_l}}$ 
only when a new label is expected. The loss function 
$\mathbb{L}\left(\mathcal{X}_{0}^{M-1}, \mathcal{Y}_{0}^{L-1}\right)$ is 
defined as follows:
   \begin{align}
     \mathbb{L}\left(\mathcal{X}_{0}^{M-1}, \mathcal{Y}_{0}^{L-1}\right) 
        = \sum_{l=0}^{L-1}  y_l \odot \log\left( \circ \, \widehat{\vec{y_l}} \right)  
          \label{eq:label_synchronous_ce_loss} 
   \end{align}
where $\odot$ and $\log \left(\circ \right)$ denote element-wise product 
(a.k.a {\it Hadamard product}) and element-wise log, respectively.

  \item {\bf Frame-synchronous inference} In this category, from the original 
target label in \eqref{eq:target_label}, we either explicitly or 
implicitly obtain the label boundaries.
In the framewise Cross Entropy (CE) training 
\cite{g_hinton_ieee_signal_processing_mag_2012_00, 
C_Kim_INTERSPEECH_2017_1, 
B_Li_INTERSPEECH_2017_1}, {\it Viterbi alignment}  
\cite{
x_huang_prentice_hall_2001_00,
l_r_rabiner_proceedings_of_ieee_1989_00} is usually employed. 
Using these alignment algorithms, 
we obtain corresponding {\it frame-synchronous }label sequences 
$\vec{z}[m] \in \mathbb{V}$ for each frame index $m$. This
latent label sequences are often called a {\it path}.
  \begin{align}
    \mathcal{Z}_{0}^{M-1}  =  
      \left\{\vec{z}[m]  \Big| 0 \le m \le M-1, \; \vec{z}[m] \in \mathbb{V} \right\}, 
    \label{eq:frame_target_label}
  \end{align}
Fig. \ref{fig:path_alignment} shows one such example. 
Such an alignment is usually called a {\it path}.

  \begin{align}
     l = \sum_{l=0}^{l=L-1}  y_l \log \left( \hat{y_l} \right)  
          \label{eq:label_synchronous_ce_loss} 
  \end{align}
\end{itemize}

Moreover, in almost all the large speech training database, the temporal boundray
of each label is not marked. In the attention-based model described in 
Sec. \ref{sec:attention_based_model} and shown in Fig. 
\ref{fig:attention_diagram}, lack of the temporal alignment information
in the training database is not a problem, since the {\it decoder} portion 
of the attention-model directly generates the output label sequences.
The loss function is also defined for each labels.

\subsection{Connectionist Temporal Classification}
\label{sec:ctc}

@@

\subsection{RNN-Transducer}
\label{sec:rnn_t}

Fig. \ref{fig:rnn_t_diagram} shows the entire structure of the  
RNN-T structure. The loss function used in RNN-T is given as follows:
\begin{align}
  P\left(\mathcal{Y}_{0}^{L-1} | \mathcal{X}_{0}^{M-1}\right) = 
    \sum_{\mathcal{Z}_{0}^{M-1} \in 
      \mathcal{A}_{CTC} 
        \left(\mathcal{X}_{0}^{M-1}, \mathcal{Y}_{0}^{L-1} \right)}
          \Pi_{m=0}^{M-1}
            P\left(\vec{z}[m] | \mathcal{X}_{0}^{M-1} \right),
\end{align}

\subsection{Attention-based model}
\label{sec:attention_based_model}

@@

\subsection{Neural Network Structure}
\label{sec:neural_network_structure}
Fig. \ref{fig:fsc_diagram} shows the entire structure of the FSC. 
As shown in this figure, LSTM layers and max-pool layers
are interleaved from the bottom layer up to the third max-pool layer.

In Fig. \ref{fig:fsc_diagram}, speech features $\vec{x}[m]$ are sampled 
at every 10 {\it ms}, which is the usual frame period in speech 
recognition
\cite{x_huang_prentice_hall_2001_00, c_kim_taslp_2016_00},
Using three two-to-one max-pool layers, $\vec{z}[p]$ has a frame period 
of 80 {\it ms}.  
The relationship between the temporal index $p$ in $\vec{z}[p]$ and 
$m$ in $\vec{x}[m]$ is given by: 
\begin{align}
  p = \lceil m / 8 \rceil \label{eq:def_p}
\end{align}
\begin{align}
  \mathcal{Z}_{0}^{M-1}  =  
    \left\{\vec{z}[m]  \Big| 0 \le m \le M-1, \; \vec{z}[m] \in \mathbb{V} \right\}, 
  \label{eq:frame_target_label}
\end{align}

@@

\subsection{Training of the Feedback Sequence Classifier}
In this section, we describe how to train FSC. As mentioned in Sec. 
\label{ref:neural_network_structure}, the FSC operates in the frame
-synchronous way. Since we do not have the alignment information

The first step is making an
alignment using the N-best alignment. The second step is updating the
neural network parameters using the Cross Entropy (CE) criterion.

@@

The first step is finding the optimal frame-synchronous sequence
$\mathcal{Z}_0^{M-1}$.

@@

\begin{figure}
  \centering
    \resizebox{100mm}{!}{
      \input{../figures/path_alignment.tex}
    } 
    \caption {
      An example of a path $\mathcal{Z}_{0}^{M-1}$ and the path movement 
      constraint shown by TODO(chanw.com)[Check the latex arrow symbol] $P -> Q$ and $P -> R$. 
      \label{fig:path_alignment}
    }
\end{figure}

In CTC in Sec. \ref{sec:ctc} and in RNN-T in Sec. \ref{sec:rnn_t}, the 
forward-backward algorithm is employed to update parameters. 
TODO(chanw.com) cite HMM tutorial paper.

For example in CTC, the forward algorithm is given by the following equation:
